---
title: "Tutorial"
#author: "Matt Galloway"
#date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = TRUE)
```

## Overview

`CVglasso` is an R package that estimates a penalized precision matrix via block-wise coordinate descent -- also known as the graphical lasso (glasso) algorithm. This package is a simple wrapper around the popular 'glasso' package and extends and enhances its capabilities. These enhancements include built-in cross validation and visualizations. A (possibly incomplete) list of functions contained in the package can be found below:

* `CVglasso()` computes the estimated precision matrix

* `plot.CVglasso()` produces a heat map or line graph for cross validation errors

See [vignette](https://mgallow.github.io/CVglasso/) or [manual](https://github.com/MGallow/CVglasso/blob/master/CVglasso.pdf).

## Installation

```{r, eval = FALSE}
# The easiest way to install is from CRAN
install.packages("CVglasso")

# You can also install the development version from GitHub:
# install.packages("devtools")
devtools::install_github("MGallow/CVglasso")
```

If there are any issues/bugs, please let me know: [github](https://github.com/MGallow/CVglasso/issues). You can also contact me via my [website](http://users.stat.umn.edu/~gall0441/). Pull requests are welcome!

## Usage

```{r, message = FALSE}
library(CVglasso)

# generate data from a sparse matrix
# first compute covariance matrix
S = matrix(0.7, nrow = 5, ncol = 5)
for (i in 1:5){
  for (j in 1:5){
    S[i, j] = S[i, j]^abs(i - j)
  }
}

# print oracle precision matrix (shrinkage might be useful)
(Omega = round(qr.solve(S), 3))

# generate 100 x 5 matrix with rows drawn from iid N_p(0, S)
set.seed(123)
Z = matrix(rnorm(100*5), nrow = 100, ncol = 5)
out = eigen(S, symmetric = TRUE)
S.sqrt = out$vectors %*% diag(out$values^0.5) %*% t(out$vectors)
X = Z %*% S.sqrt

# calculate sample covariance
Sample = (nrow(X) - 1)/nrow(X)*cov(X)

# print sample precision matrix (perhaps a bad estimate)
round(qr.solve(cov(X)), 5)


# GLASSO (lam = 0.5)
CVglasso(S = Sample, lam = 0.5)

# GLASSO cross validation
CVGLASSO = CVglasso(X, trace = "none")
CVGLASSO

# produce line graph for CV errors for GLASSO
plot(CVGLASSO)

# produce CV heat map for GLASSO
plot(CVGLASSO, type = "heatmap")

```
